\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Roopak Srivastava}

\section{Work experience}

\begin{eventlist}

\item{July,2016 -- Present}
     {Qualcomm India Pvt Ltd, Hyderabad}
     {Software Engineer}
     
Worked on design, development, debugging & optimizing of DX12 User mode driver for Video Decode of H264, HEVC Video codecs. Worked with DRM and Microsoft teams on bring-up of protected content playback using Hardware accelerated decrypt and decode for Netflix and other Protected content streaming app. Involved in optimization and debugging HW-DRM solution to achieve HEVC 4K 10 bit protected content playback on Qualcomm SoC 850.

Served as Video POC (Point of contact) for SDM835 "Windows on ARM" commercialization. Serving as POC my responsibilities involved:\hfill \break
*Interacting with Cusomer engineers and provide debug support to customer(HP).\hfill \break
*Debugging Post production issues related to video and providing fixes.\hfill \break
*Following up with teams within QC and Microsoft to get bug fixed effecting video playback and performance within alloted timeline.\hfill \break

\item{July,2015- May,2016}
     {IIT Roorkee , B.Tech Project}
     {Swarm Robotics}
     
Went through various techniques for achieving swarm intelligent robots through the use of traits of personality which will evolve due to a learning process. Proposed and simulated a prototype of an adaptive multi-agent surveillance system using a distributed control paradigm: Social Potential Fields (SPFs).

\item{2014 - 2015}
     {Electronics section, IIT Roorkee}
     {Automatic car parking}

Developed a prototype for a self-learning car parking system. During the training phase, the model tried to learn the car parking behavior when the car was parked
manually by us several times. Once the training phases was over, the learning model along with pre-defined rules was able to park a car in a given parking spot without any human intervention. The prototype won 3rd prize in Electronics section Exhibition - 2015.

\end{eventlist}
\personal
    {Flat No. 5A, Attitude Tower,\newline Timberlake Colony, Raidurgam\newline Hyderabad(500032) ,Telangana}
    {DOB : 14th September, 1993}
    {+91- 8410039912}

\section{Education}

\begin{yearlist}

\item[Electronics and communication engineering]{2012 -- 2016}
     {Bachelor of technology}
     {IIT , Roorkee}

\end{yearlist}

\section{Position of Responsibilities}

\begin{yearlist}

\item{2017 - 2018}
     {Windows video POC for snapdragon 835 commercialization.}

\item{2014 - 2015}
     {Served as Joint Secretary of Electronics section .The club nurtures need of aspiring electronics enthusiasts by means of projects and lectures. As Joint Secretary my task was to organize and deliver lectures on embedded programming, circuit design, analog electronics. Also mentored student projects helping them complete within Exhibition deadline.}

\end{yearlist}
\section{Achievements}

\begin{yearlist}

\item{2012}
     {Secured All India Rank of 1269 in Prestigious IIT-JEE exam out of approx 3 lakh aspirants }
     
\item{2015}
     {Trophy Winner of electronics awarded by hobbies club for best overall performance in Electronics section, IIT Roorkee}

\end{yearlist}

\section{Skills}

\begin{factlist}
\item{Software}{C, C++, Python, Matlab}
\item{Language}{English , Hindi}
\end{factlist}

\end{document}
